---
title: "testing"
author: "Aliceson Orbe"
date: "1/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Data Structure**
There are 28 columns and 2800 observation in this dataset, as shown below:
```{r data structure, echo = FALSE}
str(psych::bfi)
```
## *Variables*
There are 28 variables arranged in columns. Here are the names of all variables:
```{r variable names, echo = FALSE}
names(psych::bfi)
```
## *Participants*
There are 2800 participants in this dataset. Each row represents one participant.
```{r number of rows, echo = FALSE}
nrow(psych::bfi)
```
### *Age*
The mean age of participant is:
```{r mean age, echo = FALSE}
mean(psych::bfi$age)
```
With a Standard Deviation of:
```{r SD age, echo = FALSE}
sd(psych::bfi$age)
```
### *Sex*
There are twice as many females as males in this dataset.

_\*The following functions were inspired by [RoyalTS's](https://stackoverflow.com/questions/23000661/how-to-realize-countifs-function-excel-in-r/23000756) answer on Stack OverFlow\*_

The number of males in the dataset is:
```{r number of males, echo = FALSE}
sum(psych::bfi$gender == '1', na.rm=TRUE)
```
The number of females in the dataset is:
```{r number of females, echo = FALSE}
sum(psych::bfi$gender == '2', na.rm=TRUE)
```